### 2013-09-18 Paper_Markdown.Rmd
Major changes.  Plotting changes in the paper markdown, added libraries in `data_setup.R`, `bootstrap_mat.R` now works and has output `mat.res.RData`, which should be the final output.  `bootstrap_mat.R` is pretty fast as a parallel process.  Cleaned up `bootstrap_wa.R`.
Should have pushed this as a small set of changes, sorry.

```{r}
source('R/data_setup.R')

@@

```{r SiteLocations, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations'}
plot(climate[,2:3], pch=19, cex=0.6, col=rgb(0.1, 0.1, 0.1, 0.3))

mds <- data.frame(pol.mds$points)

ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point(alpha=0.5, size = 2) + theme_bw() +
  xlab('MDS Axis One') + ylab('MDS Axis Two') +
    theme(text = element_text(size=24, family='serif'))

@@

>>>>

```{r}

source('R/data_setup.R')

@@

```{r SiteLocations, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations'}
map <- map_data('world')

ggplot(data = map, aes(long, lat, group=group)) + geom_path(color='black') +
   coord_map(xlim=c(-170, -40), ylim=c(20, 83))

plot(climate[,2:3], pch=19, cex=0.6, col=rgb(0.1, 0.1, 0.1, 0.3))

@@

```
Figure X.  Distribution of squared-chord dissimilarity values.  The 95% confidence interval for the minumum spanning distance in the North American Modern Pollen Database is 0.10 - 0.48.  We choose 0.48 as our cut-off for 'non-analogue' distances in the database.

mds <- data.frame(pol.mds$points,
                  non.ana = factor(min.diss > 0.48))

ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point(alpha=0.5, size = 4, aes(color = non.ana)) + theme_bw() +
  xlab('MDS Axis One') + ylab('MDS Axis Two') +
    theme(text = element_text(size=24, family='serif'))
